%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{cv_12} % Use US Letter paper, change to a4paper for A4

\begin{document}

%----------------------------------------------------------------------------------------
%	FIRST PAGE
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated% Print the Last Updated text at the top right
\pagecounter% Print the Page number text at the top right

\namesection{Sinisa}{Petkovic}{
    \href{mailto:sini.petkovic@gmail.com}{sini.petkovic@gmail.com}
    \textbullet{}
    \href{https://sinisapetkovic.com}{sinisapetkovic.com} \textbullet{}
    905.745.4734
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.39\textwidth}% The left column takes up 39% of the text width of the page

    %------------------------------------------------
    %	LINKS
    %------------------------------------------------

    \section{Links}

    \href{https://github.com/cile-bgd}{\bf GitHub} \textbullet{}
    \href{https://www.linkedin.com/in/sinisa-petkovic-b704034/}{\bf
        LinkedIn} \textbullet{}
    \href{https://twitter.com/SinisaPetkovic}{\bf Twitter} \textbullet{}
    \href{https://c.im/@foontzoot}{\bf Mastodon}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------
    %	SKILLS
    %------------------------------------------------

    \section{Skills}

    \subsection{Programming}

    C\# \textbullet{} JS/TS \textbullet{} GO \textbullet{} C/C++
    \textbullet{} Python \textbullet{} Scala \textbullet{} Git\\
    Rust \textbullet{} SQL \textbullet{} OOP \textbullet{} SOLID
    \textbullet{} Design Patterns\\
    Data Structures \textbullet{} Bash \textbullet{} Powershell

    \sectionspace% Some whitespace after the section

    \subsection{Front-end}

    React \textbullet{} Angular \textbullet{} Flutter \textbullet{} Redux
    \textbullet{} NgRx \textbullet{} WPF\\
    HTML/CSS \textbullet{} HTMX \textbullet{} MUI \textbullet{} PrimeNG
    \textbullet{} MAUI\\
    AvaloniaUI \textbullet{} Razor Pages \textbullet{} WebForms
    \textbullet{} SVG\\
    Markdown \textbullet{} \LaTeX\ \textbullet{} AsposePDF \textbullet{}
    Adobe

    \sectionspace% Some whitespace after the section

    \subsection{Back-end}

    \dotnet\ / \dotnet\ Core \textbullet{} REST API \textbullet{} MVC
    \textbullet{} Docker\\
    Node/Express \textbullet{} WCF/SOAP \textbullet{} gRPC \textbullet{}
    Django\\
    Swagger \textbullet{} OAuth \textbullet{} Spring \textbullet{}
    WebAssembly

    \sectionspace% Some whitespace after the section

    \subsection{.NET/.NET Core}

    Threading \textbullet{} Delegates \textbullet{} Events \textbullet{}
    Generics\\
    Collections \textbullet{} Exceptions \textbullet{} Transactions\\
    Reflection \textbullet{} Serialization \textbullet{} EF/EF Core
    \textbullet{} Dapper\\
    LINQ \textbullet{} CQRS \textbullet{} MSMQ \textbullet{} IoC/DI
    \textbullet{} MediatR\\
    WinForms \textbullet{} WebForms \textbullet{} FluentValidations\\
    SignalR \textbullet{} Identity \textbullet{} xUnit/nUnit

    \sectionspace% Some whitespace after the section

    \subsection{Databases/Storage}

    SQL Server \textbullet{} Azure SQL \textbullet{} MySQL \textbullet{}
    Oracle\\
    PostgreSQL \textbullet{} CosmosDB \textbullet{} DynamoDB \textbullet{}
    SQLite\\
    MongoDB \textbullet{} Firebase \textbullet{} Redis \textbullet{} neo4j
    \textbullet{} CouchDB

    \sectionspace% Some whitespace after the section

    \subsection{MS Azure}

    Functions/Durable Functions \textbullet{} Service Bus\\
    KeyVault \textbullet{} Table/Blob/Queue Storage \textbullet{} AD\\
    App. Insights \textbullet{} Cognitive Search \textbullet{} DevOps\\
    Api Management \textbullet{} App Service \textbullet{} DataFactory

    \sectionspace% Some whitespace after the section

    \subsection{AWS}

    IAM \textbullet{} EC2 \textbullet{} S3 \textbullet{} Lambda
    \textbullet{} SQS \textbullet{} SNS \textbullet{} Aurora\\
    Event Bridge \textbullet{} Secrets Manager \textbullet{} Code
    Pipeline\\
    Cloud Watch \textbullet{} Step Functions \textbullet{} API Gateway

    \sectionspace% Some whitespace after the section

    %------------------------------------------------
    %	EDUCATION
    %------------------------------------------------

    \section{Education}

    \subsection{University of Belgrade}

    \descript{Faculty of Mathematics}
    \location{1994 | Belgrade, Serbia}

    \sectionspace% Some whitespace after the section

    \descript{Bachelor's degree in mathematics}

    \sectionspace% Some whitespace after the section

    %----------------------------------------------------------------------------------------
    %	END LEFT COLUMN
    %----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.59\textwidth}% The right column takes up 59% of the text width of the page

    %------------------------------------------------
    %	EXPERIENCE
    %------------------------------------------------

    \section{Experience}

    \sectionspace% Some whitespace after the section

    \runsubsection{LawPRO}
    \descript{| Senior Software Engineer, Consultant}

    \location{Nov 2021 — Present | (Remote) Toronto, ON}
    \vspace{\topsep}
    \begin{tightitemize}
        \item Back-end development in \dotnet\ Core, C\#, CQRS,
        MediatR, Go, Lambda, API Gateway, RDS Aurora (MySQL), Okta OAuth2.
        \item Front-end development in React, Redux, React Hooks, and
        MUI.\@
        \item Migrated \dotnet\ Core 3.1 to \dotnet\ 6, Node v13 to
        Node v18, and Code Pipeline to GitHub Actions.
        \item Delivered effective User Profile solution, solving the
        data sync issues between Okta and LawPRO services.
        \item Introduced data aggregation solution for local and
        Azure-based PowerBI reporting solutions.
        \item Participated in software releases and regression testing.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    \runsubsection{PwC (Infosys)}
    \descript{| Tech Lead, Consultant}

    \location{Aug 2021 — Nov 2021 | (Remote) Oakville, ON}
    \begin{tightitemize}
        \item Helped design, build and maintain PwC Global Compliance Service.
        \item Created and refactored RESTful APIs following SOLID
        principles.
        \item Front-end development in Angular 10+ with PrimeNG and
        NgRx.
        \item Refactored Ng services to return data to models, avoiding
        \verb|any| type.
        \item Introduced unit testing in SQL Server Database Solution.
        \item Altered and created stored procedures to work seamlessly
        with Dapper.
        \item Introduced Tech-Debt stories/features to improve code
        quality.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    \runsubsection{Freedom Mobile}
    \descript{| Senior Software Engineer, Consultant}

    \location{May 2021 — Aug 2021 | (Remote) Toronto, ON}
    \begin{tightitemize}
        \item Converted numerous API calls to AWS API Gateway with
        Lambdas, PostgreSQL and DynamoDB.\@
        \item Refactored monolithic back-end solution into
        microservices-ready solution following SOLID principles.\@
        \item Created NuGet packages from extracted libraries and made
        them available on AWS CodeArtifact.
        \item Recreated PostgreSQL database based on existing on-prem
        SQL Server schema using EF code-first method.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    \runsubsection{autoTRADER}
    \descript{| Senior Software Engineer, Consultant}

    \location{Sep 2020 — Apr 2021 | (Remote) Toronto, ON}
    \begin{tightitemize}
        \item Successfully created, tested, and released Azure Durable
        Function to back up and clear old ads from CosmosDB, SQLServer, Table
        and Blob
        Storage, and Search Indexes — cleared more than 4.5 million old
        entries.\@
        \item Worked on numerous data transformation projects utilizing
        Table Storage, Queue Storage, Functions, Durable Functions, Service
        Bus, Data
        Factory, Cosmos DB, SQL Server, and MySQL.\@
        \item Excelled at clearing the tech debt, refactoring, and
        version upgrades.
        \item Created/upgraded several CI/CD pipelines on Azure DevOps.
        \item Fixed several bugs in the front-end React application.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    %----------------------------------------------------------------------------------------
    %	END RIGHT COLUMN
    %----------------------------------------------------------------------------------------

\end{minipage}% The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated% Print the Last Updated text at the top right
\pagecounter% Print the Page number text at the top right

\namesection{Sinisa}{Petkovic}{
    \href{mailto:sini.petkovic@gmail.com}{sini.petkovic@gmail.com}
    \textbullet{}
    \href{https://sinisapetkovic.com}{sinisapetkovic.com} \textbullet{}
    905.745.4734
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.39\textwidth} % The left column takes up 339% of the text width of the page

    %----------------------------------------------------------------------------------------
    %	ITEMIZED
    %----------------------------------------------------------------------------------------

    \section{Itemized}

    % \runsubsection{Available upon request}
    C\# \\
    JavaScript \\
    TypeScript \\
    Go \\
    Python \\
    PHP \\
    Java/Scala \\
    C/C++ \\
    SQL/T-SQL \\
    Erlang \\
    Elixir \\
    Rust \\

    \sectionspace% Some whitespace after the section
    
    %----------------------------------------------------------------------------------------
    %	REFERENCES
    %----------------------------------------------------------------------------------------

    \section{References}

    \runsubsection{Available upon request}

    \sectionspace% Some whitespace after the section

    %----------------------------------------------------------------------------------------
    %	END LEFT COLUMN
    %----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.59\textwidth}% The right column takes up 59% of the text width of the page

    %----------------------------------------------------------------------------------------
    %	EXPERIENCE
    %----------------------------------------------------------------------------------------

    \section{Experience}

    \runsubsection{Toyota Motor Manufacturing Canada}
    \descript{| Software Developer}

    \location{Mar 2020 — Sep 2020 | Cambridge, ON}
    \vspace{\topsep}
    \begin{tightitemize}
        \item Created, maintained, and troubleshot ASP.NET WEB API, Angular,
        WPF, and Oracle PL/SQL queries.
        \item Replaced MSMQ services with Azure Service Bus and Azure Queue.
        \item Migrated codebase with changelog history from SVN to Git on Azure
        DevOps.
        \item Converted legacy DLL files into NuGet packages and created
        internal feed on Azure Pipelines.
        \item Created Oracle 10G to PostgreSQL migration program
        with Python.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------

    \runsubsection{Indellient}
    \descript{| Full-stack Developer, Consultant}

    \location{Sep 2019 — Mar 2020 | Oakville, ON}
    \begin{tightitemize}
        \item Helped design, build and maintain OSG's integrated solutions.
        \item Created serverless functions with AWS Lambda.
        \item Extensively used jQuery Data Tables for data presentation and
        manipulation.
        \item Upgraded and optimized multiple ETL packages.
        \item Migrated \dotnet\ Core and EF Core from version 2.2 to 3.1.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------

    \runsubsection{Bond Brand Loyalty}
    \descript{| Senior Full-stack Developer, Consultant}

    \location{Nov 2018 — Sep 2019 | Mississauga, ON}
    \begin{tightitemize}
        \item Helped build and maintain Ford Canada's internal sales and
        service web applications.
        \item Upgraded daily manual data import process from various SQL Server
        jobs, SSIS packages and custom ASP.NET solutions to automated process using
        Azure Logic Apps, Service Bus, Functions and Storage.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------

    \runsubsection{Titus Inc.}
    \descript{| Software Developer}

    \location{Aug 2018 — Nov 2018 | (Remote) Ottawa, ON}
    \begin{tightitemize}
        \item Designed and built Office Addon solution on
        ASP.NET Core, NodeJS/TS, OAuth2, SignalR and Kestrel.
        \item Created QT/C++ wrapper for existing \dotnet\ Core application
        running in Linux.
        \item Introduced front-end tests with Mocha, Istanbul and NYC,
        and helped create private npm repository.
        \item Participated in weekly code quality meetings, displaying
        and explaining SonarQube reports.
    \end{tightitemize}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------

    \runsubsection{Questica}
    \descript{| Software Developer}

    \location{Oct 2016 — Aug 2018 | Burlington, ON}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------

    \runsubsection{The Hunt Group}
    \descript{| Lead Software Developer}

    \location{Mar 2007 — Oct 2016 | Mississauga, ON}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------

    \runsubsection{Cryptologic Inc.}
    \descript{| C++/MFC Client Side Software Developer}

    \location{Jan 2006 — Mar 2007 | Toronto, ON}

    \sectionspace% Some whitespace after the section

    %------------------------------------------------

    %----------------------------------------------------------------------------------------

\end{minipage}

\end{document}
